---
title: "Myocardin splicing: differential exon usage analysis"
author:
   name: "Dmytro Kryvokhyzha"
   email: dmytro.kryvokhyzha@med.lu.se
   affiliation: LUDC Bioinformatics Unit
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:    
    code_folding: show
    toc: true
---
    
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, eval=TRUE)
knitr::opts_knit$set(root.dir = '../')
```

## Dependencies

```{r, message=FALSE, eval=TRUE}
library(DEXSeq)
library(BiocParallel)
# library(RColorBrewer)
# library(ggplot2)
# library(mygene)
# library(sm)
# library(reshape2)
```

## Data

Load the counts:

```{r}
countFiles <- list.files('results/tables/DEXSeq/', full.names=TRUE)
sampleTable <- data.frame(row.names = c("CMV1", "CMV2", "CMV4", "CMV5",
                                        "MYO1", "MYO2", "MYO4", "MYO5"),
                          condition = c(rep('control', 4), rep('treatment', 4)))
flattenedFile <- 'intermediate/DEXSeq/gencode.v35.primary_assembly.annotation.DEXSeq.gtf'
countFiles <- 
dxd <- DEXSeqDataSetFromHTSeq(countFiles,
                              sampleData=sampleTable,
                              design= ~ sample + exon + condition:exon,
                              flattenedfile=flattenedFile)
colData(dxd)
```

Subset data for development
```{r}
dxd <- dxd[sample(nrow(dxd), 10000), ]
```


Counts:

```{r}
head(featureCounts(dxd), 5)
```

Print the first 3 lines of the feature data annotation:

```{r}
head(rowRanges(dxd), 3)
```

Check the design:

```{r}
sampleAnnotation(dxd)
```


Exon counts are split into two categoris. 
The first 8 columns correspond to the number of reads mapping to 
out exonic regions and the last 8 columns correspond to the sum of the counts 
mapping to the rest of the exons from the same gene on each sample.

```{r}
head(counts(dxd), 5 )
split(seq_len(ncol(dxd)), colData(dxd)$exon )
```


## Normalisation & dispersion estimation

The same method as in DESeq2:

```{r}
ncores <- MultiCoreParam(6)
dxd <- estimateSizeFactors(dxd, BPPARAM=ncores)
dxd <- estimateDispersions(dxd, BPPARAM=ncores)
```

Plot disprrssion:

```{r}
plotDispEsts(dxd)
```

## Differential exon usage

*DEXSeq* fits a generalized linear model with the formula 
`~ sample + exon + condition:exon` and compare it to the null model) `~ sample + exon`.
The deviances of both fits are compared using a χ2-distribution, providing a p value.

We test whether the fraction of the genes reads that fall onto the exon under the test 
differs significantly between the experimental conditions.

```{r}
ncores <- MulticoreParam(6)
dxr <- DEXSeq(dxd, BPPARAM=ncores)
```

Results:

```{r}
head(dxr, 5)
```

Description of each column:

```{r}
mcols(dxr)$description
```

How many exonic exons are significant with a false discovery rate of 1%?

```{r}
sum(dxr$padj < 0.01, na.rm = T)
```

How many genes are affected?

```{r}
sum(tapply(dxr$padj < 0.01, dxr$groupID, any), na.rm = T)
```

```{r}
plotMA(dxr, cex=1)
```

## Visualization

```{r}
head(dxr[order(dxr$padj),'groupID'])
```

```{r}
plotDEXSeq(dxr, "ENSG00000065534.19",
           legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
```

## FDR at the gene level

DEXSeq returns one p-value for each exonic region.
However, sometimes it is informative to know what is the FDR at the gene level,
i.e. knowing the numer of genes with at least one differentially used exon
while keeping control of FDR.

```{r}
numbOfGenes <- sum( perGeneQValue(dxr) < 0.01)
numbOfGenes
```

## Preprocessing using featureCounts

See https://github.com/vivekbhr/Subread_to_DEXSeq. It seems like there is no benefits
of using featureCounts with DEXSeq.
