---
title: "Myocardin splicing: WebGestaltR enrichment analysis"
author:
  name: "Dmytro Kryvokhyzha"
email: dmytro.kryvokhyzha@med.lu.se
affiliation: LUDC Bioinformatics Unit
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  toc: true
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=TRUE)
knitr::opts_knit$set(root.dir = '../')
```

## Dependencies

```{r, message=FALSE, eval=TRUE}
library(WebGestaltR)
repor_dir <- 'results/reports/WebGestaltR'
```

## Data

### DESeq2

Load

```{r}
DESeqD <- read.table('results/tables/DESeq/DESeq_all.csv',
                  sep = "\t", header = T)
DESeqGSEA <- DESeqD[,c("gene", "log2FoldChange")]
DESeqGSEA$gene <- gsub("\\..*","", DESeqGSEA$gene)
DESeqGSEA <- na.omit(DESeqGSEA[order(DESeqGSEA$log2FoldChange, decreasing = T),])
```

### DEXSeq

Get genes for FDR<0.01:
 
```{bash, eval=FALSE}
mkdir -p intermediate/WebGestaltR/

awk '$2<=0.01' results/tables/DEXSeq/DEXSeq_results_geneFDR.csv \
  > intermediate/WebGestaltR/DEXSeq_results_geneFDR0.01.csv
  
python code/DEXSeq_to_genes.py \
  -i intermediate/WebGestaltR/DEXSeq_results_geneFDR0.01.csv \
  -c gene_level_FDR \
  -o intermediate/WebGestaltR/DEXSeq_results_FDR0.01genes.csv

python code/DEXSeq_to_genes.py \
  -i results/tables/DEXSeq/DEXSeq_results_geneFDR.csv \
  -c gene_level_FDR \
  -o intermediate/WebGestaltR/DEXSeq_results_FDRgenes.csv
```

Load the data:

```{r, eval=FALSE}
dDE <- read.table('intermediate/WebGestaltR/DEXSeq_results_FDR0.01genes.csv',
                  sep = "\t", header = T)
dall <- read.table('intermediate/WebGestaltR/DEXSeq_results_FDRgenes.csv',
                   sep = "\t", header = T)
```

Create lists:

```{r, eval=FALSE}
DEgene <- gsub("\\..*","", dDE$gene)
Allgene <- gsub("\\..*","", dall$gene)
length(DEgene)
length(Allgene)
```

### rMATS

```{r, eval=FALSE}
rmats_fdr <- 0.05
Jtype <- c("A3SS", "A5SS", "SE", "RI", "MXE")
rmats_sign <- c()
rmats_all <- c()
for (i in Jtype){
   #i <- "SE"
   d <- read.table(paste('results/tables/rMATS/rMATS_sign_', i, '.csv', sep = ""),
                   header = T, sep = "\t", stringsAsFactors=F)
   rmats_sign <- unique(c(rmats_sign, gsub("\\..*","", as.character(d$GeneID))))
   d2 <- read.table(paste('results/tables/rMATS/rMATS_all_', i, '.csv', sep = ""),
                   header = T, sep = "\t", stringsAsFactors=F)
   rmats_all <- unique(c(rmats_all, gsub("\\..*","", as.character(d2$GeneID))))
}
length(rmats_sign)
length(rmats_all)
```

### ISA

```{r, eval=FALSE}
isa_fdr <- 0.05
isa_All <- read.table('results/tables/IsoformSwitchAnalyzeR/isoformSwitchAnalysis.csv',
                      header = T, sep = '\t')
isa_ref <- read.table('results/tables/IsoformSwitchAnalyzeR/isoformSwitchAnalysis_ref_genes.csv',
                      header = T, sep = '\t')
isa_sing <- na.omit(unique(as.character(isa_All$gene_id[which(isa_All$padj <= isa_fdr)])))
isa_sing <- unique(gsub("\\..*","", isa_sing))
isa_all <- unique(gsub("\\..*","", as.character(isa_ref$x)))
length(isa_sing)
length(isa_all)
```

## Enrichment

### DESeq2

#### KEGG

```{r}
DESeq2_gsea_kegg <- WebGestaltR(interestGene = DESeqGSEA,
                        interestGeneType = "ensembl_gene_id",
                        referenceGeneType = "ensembl_gene_id",
                        enrichMethod = "GSEA",
                        organism = "hsapiens",
                        enrichDatabase = 'pathway_KEGG',
                        sigMethod = "fdr",
                        fdrMethod = "BH",
                        fdrThr = 0.05,
                        reportNum = 30,
                        minNum = 5,
                        maxNum = 2000,
                        isOutput = TRUE,
                        outputDirectory = repor_dir,
                        projectName = 'DESeq2_GSEA_KEGG',
                        nThreads = 8)
DESeq2_gsea_kegg <- DESeq2_gsea_kegg[order(DESeq2_gsea_kegg$enrichmentScore, decreasing = T),]
knitr::kable(head(DESeq2_gsea_kegg[,c('description', 'enrichmentScore', 'FDR')]))
```

#### GO

```{r}
DESeq2_gsea_go <- WebGestaltR(interestGene = DESeqGSEA,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "GSEA",
                      organism = "hsapiens",
                      enrichDatabase = c('geneontology_Biological_Process_noRedundant',
                                         'geneontology_Cellular_Component_noRedundant',
                                         'geneontology_Molecular_Function_noRedundant'),
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DESeq2_GSEA_GO',
                      nThreads = 8)
DESeq2_gsea_go <- DESeq2_gsea_go[order(DESeq2_gsea_go$enrichmentScore, decreasing = T),]
knitr::kable(head(DESeq2_gsea_go[,c('description', 'enrichmentScore', 'FDR')]))
```

#### Panther

```{r}
DESeq2_gsea_Panther <- WebGestaltR(interestGene = DESeqGSEA,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "GSEA",
                      organism = "hsapiens",
                      enrichDatabase = 'pathway_Panther',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DESeq2_GSEA_Panther',
                      nThreads = 8)
DESeq2_gsea_Panther <- DESeq2_gsea_Panther[order(DESeq2_gsea_Panther$enrichmentScore, decreasing = T),]
knitr::kable(head(DESeq2_gsea_Panther[,c('description', 'enrichmentScore', 'FDR')]))
```

#### Reactome

```{r}
DESeq2_gsea_Reactome <- WebGestaltR(interestGene = DESeqGSEA,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "GSEA",
                      organism = "hsapiens",
                      enrichDatabase = 'pathway_Reactome',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DESeq2_GSEA_Reactome',
                      nThreads = 8)
DESeq2_gsea_Reactome <- DESeq2_gsea_Reactome[order(DESeq2_gsea_Reactome$enrichmentScore, decreasing = T),]
knitr::kable(head(DESeq2_gsea_Reactome[,c('description', 'enrichmentScore', 'FDR')]))
```

#### Wikipathway

```{r}
DESeq2_gsea_Wikipathway <- WebGestaltR(interestGene = DESeqGSEA,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "GSEA",
                      organism = "hsapiens",
                      enrichDatabase = 'pathway_Wikipathway',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DESeq2_GSEA_Wikipathway',
                      nThreads = 8)
DESeq2_gsea_Wikipathway <- DESeq2_gsea_Wikipathway[order(DESeq2_gsea_Wikipathway$enrichmentScore, decreasing = T),]
knitr::kable(head(DESeq2_gsea_Wikipathway[,c('description', 'enrichmentScore', 'FDR')]))
```

#### CORUM

```{r}
DESeq2_gsea_CORUM <- WebGestaltR(interestGene = DESeqGSEA,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "GSEA",
                      organism = "hsapiens",
                      enrichDatabase = 'network_CORUM',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DESeq2_GSEA_CORUM',
                      nThreads = 8)
DESeq2_gsea_CORUM <- DESeq2_gsea_CORUM[order(DESeq2_gsea_CORUM$enrichmentScore, decreasing = T),]
knitr::kable(head(DESeq2_gsea_CORUM[,c('description', 'enrichmentScore', 'FDR')]))
```

#### CORUMA

```{r}
DESeq2_gsea_CORUMA <- WebGestaltR(interestGene = DESeqGSEA,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "GSEA",
                      organism = "hsapiens",
                      enrichDatabase = 'network_CORUMA',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DESeq2_GSEA_CORUMA',
                      nThreads = 8)
DESeq2_gsea_CORUMA <- DESeq2_gsea_CORUMA[order(DESeq2_gsea_CORUMA$enrichmentScore, decreasing = T),]
knitr::kable(head(DESeq2_gsea_CORUMA[,c('description', 'enrichmentScore', 'FDR')]))
```

#### phenotype_Human_Phenotype_Ontology

R crashes.

```{r}
DESeq2_gsea_Phenotype <- WebGestaltR(interestGene = DESeqGSEA,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "GSEA",
                      organism = "hsapiens",
                      enrichDatabase = 'phenotype_Human_Phenotype_Ontology',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DESeq2_GSEA_Phenotype',
                      nThreads = 1)
DESeq2_gsea_Phenotype <- DESeq2_gsea_Phenotype[order(DESeq2_gsea_Phenotype$enrichmentScore, decreasing = T),]
knitr::kable(head(DESeq2_gsea_Phenotype[,c('description', 'enrichmentScore', 'FDR')]))
```

#### MuscleGeneSets (fix error)

Fails with the error `Error in plot.new() : figure margins too large`.
```{r}
par(mar=c(0,0,0,0))
DESeq2_gsea_MuscleGeneSets <- WebGestaltR(interestGene = DESeqGSEA,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "GSEA",
                      organism = "hsapiens",
                      enrichDatabase = 'community-contributed_MuscleGeneSets_Duddy_2017',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 10,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DESeq2_GSEA_MuscleGeneSets',
                      nThreads = 8)
DESeq2_gsea_MuscleGeneSets <- DESeq2_gsea_MuscleGeneSets[order(DESeq2_gsea_MuscleGeneSets$enrichmentScore, decreasing = T),]
knitr::kable(head(DESeq2_gsea_MuscleGeneSets[,c('description', 'enrichmentScore', 'FDR')]))
```

### DEXSeq

#### KEGG

```{r}
ora_kegg <- WebGestaltR(interestGene = DEgene,
                        referenceGene = Allgene,
                        interestGeneType = "ensembl_gene_id",
                        referenceGeneType = "ensembl_gene_id",
                        enrichMethod = "ORA",
                        organism = "hsapiens",
                        enrichDatabase = 'pathway_KEGG',
                        sigMethod = "fdr",
                        fdrMethod = "BH",
                        fdrThr = 0.05,
                        reportNum = 30,
                        minNum = 5,
                        maxNum = 2000,
                        isOutput = TRUE,
                        outputDirectory = repor_dir,
                        projectName = 'DEXSeq_geneFDR0.01_ORA_KEGG',
                        nThreads = 8)
ora_kegg <- ora_kegg[order(ora_kegg$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_kegg[,c('description', 'enrichmentRatio')]))
```

#### GO

```{r}
ora_go <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = c('geneontology_Biological_Process_noRedundant',
                                         'geneontology_Cellular_Component_noRedundant',
                                         'geneontology_Molecular_Function_noRedundant'),
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_GO',
                      nThreads = 8)
ora_go <- ora_go[order(ora_go$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_go[,c('description', 'enrichmentRatio')]))
```

#### Panther

```{r}
ora_Panther <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'pathway_Panther',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_Panther',
                      nThreads = 8)
ora_Panther <- ora_Panther[order(ora_Panther$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_Panther[,c('description', 'enrichmentRatio')]))
```

#### Reactome

```{r}
ora_Reactome <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'pathway_Reactome',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_Reactome',
                      nThreads = 8)
ora_Reactome <- ora_Reactome[order(ora_Reactome$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_Reactome[,c('description', 'enrichmentRatio')]))
```

#### Wikipathway

```{r}
ora_Wikipathway <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'pathway_Wikipathway',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_Wikipathway',
                      nThreads = 8)
ora_Wikipathway <- ora_Wikipathway[order(ora_Wikipathway$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_Wikipathway[,c('description', 'enrichmentRatio')]))
```

#### CORUM

```{r}
ora_CORUM <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'network_CORUM',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_CORUM',
                      nThreads = 8)
ora_CORUM <- ora_CORUM[order(ora_CORUM$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_CORUM[,c('description', 'enrichmentRatio')]))
```

#### CORUMA

```{r}
ora_CORUMA <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'network_CORUMA',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_CORUMA',
                      nThreads = 8)
ora_CORUMA <- ora_CORUMA[order(ora_CORUMA$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_CORUMA[,c('description', 'enrichmentRatio')]))
```

#### phenotype

```{r}
ora_Phenotype <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'phenotype_Human_Phenotype_Ontology',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_Phenotype',
                      nThreads = 8)
ora_Phenotype <- ora_Phenotype[order(ora_Phenotype$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_Phenotype[,c('description', 'enrichmentRatio')]))
```

#### MuscleGeneSets

```{r}
ora_MuscleGeneSets <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'community-contributed_MuscleGeneSets_Duddy_2017',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_MuscleGeneSets',
                      nThreads = 8)
ora_MuscleGeneSets <- ora_MuscleGeneSets[order(ora_MuscleGeneSets$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_MuscleGeneSets[,c('geneSet', 'enrichmentRatio')]))
```

### rMATS

No significant enrichment.

#### KEGG

```{r}
rmats_kegg <- WebGestaltR(interestGene = rmats_sign,
                        referenceGene = rmats_all,
                        interestGeneType = "ensembl_gene_id",
                        referenceGeneType = "ensembl_gene_id",
                        enrichMethod = "ORA",
                        organism = "hsapiens",
                        enrichDatabase = 'pathway_KEGG',
                        sigMethod = "fdr",
                        fdrMethod = "BH",
                        fdrThr = 0.05,
                        reportNum = 30,
                        minNum = 5,
                        maxNum = 2000,
                        isOutput = TRUE,
                        outputDirectory = repor_dir,
                        projectName = 'rMATS_geneFDR0.05_ORA_KEGG',
                        nThreads = 8)
rmats_kegg <- rmats_kegg[order(rmats_kegg$enrichmentRatio, decreasing = T),]
knitr::kable(head(rmats_kegg[,c('description', 'enrichmentRatio')]))
```

#### GO

```{r}
rmats_go <- WebGestaltR(interestGene = rmats_sign,
                      referenceGene = rmats_all,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = c('geneontology_Biological_Process_noRedundant',
                                         'geneontology_Cellular_Component_noRedundant',
                                         'geneontology_Molecular_Function_noRedundant'),
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'rMATS_geneFDR0.05_ORA_GO',
                      nThreads = 8)
rmats_go <- rmats_go[order(rmats_go$enrichmentRatio, decreasing = T),]
knitr::kable(head(rmats_go[,c('description', 'enrichmentRatio')]))
```

### ISA

#### KEGG

```{r}
isa_kegg <- WebGestaltR(interestGene = isa_sing,
                        referenceGene = isa_all,
                        interestGeneType = "ensembl_gene_id",
                        referenceGeneType = "ensembl_gene_id",
                        enrichMethod = "ORA",
                        organism = "hsapiens",
                        enrichDatabase = 'pathway_KEGG',
                        sigMethod = "fdr",
                        fdrMethod = "BH",
                        fdrThr = 0.05,
                        reportNum = 30,
                        minNum = 5,
                        maxNum = 2000,
                        isOutput = TRUE,
                        outputDirectory = repor_dir,
                        projectName = 'ISA_geneFDR0.05_ORA_KEGG',
                        nThreads = 8)
isa_kegg <- isa_kegg[order(isa_kegg$enrichmentRatio, decreasing = T),]
knitr::kable(head(isa_kegg[,c('description', 'enrichmentRatio')]))
```

#### GO

```{r}
isa_go <- WebGestaltR(interestGene = isa_sing,
                      referenceGene = isa_all,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = c('geneontology_Biological_Process_noRedundant',
                                         'geneontology_Cellular_Component_noRedundant',
                                         'geneontology_Molecular_Function_noRedundant'),
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'ISA_geneFDR0.05_ORA_GO',
                      nThreads = 8)
isa_go <- isa_go[order(isa_go$enrichmentRatio, decreasing = T),]
knitr::kable(head(isa_go[,c('description', 'enrichmentRatio')]))
```

```{bash, include=F, eval=T}
rename.ul 'Project_' "" results/reports/WebGestaltR/Project_*
```
