---
title: "Myocardin splicing: WebGestaltR enrichment analysis"
author:
  name: "Dmytro Kryvokhyzha"
email: dmytro.kryvokhyzha@med.lu.se
affiliation: LUDC Bioinformatics Unit
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  toc: true
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=TRUE)
knitr::opts_knit$set(root.dir = '../')
```

## Dependencies

```{r, message=FALSE, eval=TRUE}
library(WebGestaltR)
repor_dir <- 'results/reports/WebGestaltR'
```

## Data

Get genes for FDR<0.01:
 
```{bash, eval=FALSE}
mkdir -p intermediate/WebGestaltR/

awk '$2<=0.01' results/tables/DEXSeq/DEXSeq_results_geneFDR.csv \
  > intermediate/WebGestaltR/DEXSeq_results_geneFDR0.01.csv
  
python code/DEXSeq_to_genes.py \
  -i intermediate/WebGestaltR/DEXSeq_results_geneFDR0.01.csv \
  -c gene_level_FDR \
  -o intermediate/WebGestaltR/DEXSeq_results_FDR0.01genes.csv

python code/DEXSeq_to_genes.py \
  -i results/tables/DEXSeq/DEXSeq_results_geneFDR.csv \
  -c gene_level_FDR \
  -o intermediate/WebGestaltR/DEXSeq_results_FDRgenes.csv
```

Load the data:

```{r}
dDE <- read.table('intermediate/WebGestaltR/DEXSeq_results_FDR0.01genes.csv',
                  sep = "\t", header = T)
dall <- read.table('intermediate/WebGestaltR/DEXSeq_results_FDRgenes.csv',
                   sep = "\t", header = T)
```

Create lists:

```{r}
DEgene <- gsub("\\..*","", dDE$gene)
Allgene <- gsub("\\..*","", dall$gene)
length(DEgene)
length(Allgene)
```

## Enrichment

### KEGG

```{r}
ora_kegg <- WebGestaltR(interestGene = DEgene,
                        referenceGene = Allgene,
                        interestGeneType = "ensembl_gene_id",
                        referenceGeneType = "ensembl_gene_id",
                        enrichMethod = "ORA",
                        organism = "hsapiens",
                        enrichDatabase = 'pathway_KEGG',
                        sigMethod = "fdr",
                        fdrMethod = "BH",
                        fdrThr = 0.05,
                        reportNum = 30,
                        minNum = 5,
                        maxNum = 2000,
                        isOutput = TRUE,
                        outputDirectory = repor_dir,
                        projectName = 'DEXSeq_geneFDR0.01_ORA_KEGG',
                        nThreads = 8)
ora_kegg <- ora_kegg[order(ora_kegg$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_kegg[,c('description', 'enrichmentRatio')]))
```

### GO

```{r}
ora_go <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = c('geneontology_Biological_Process_noRedundant',
                                         'geneontology_Cellular_Component_noRedundant',
                                         'geneontology_Molecular_Function_noRedundant'),
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_GO',
                      nThreads = 8)
ora_go <- ora_go[order(ora_go$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_go[,c('description', 'enrichmentRatio')]))
```

### Panther

```{r}
ora_Panther <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'pathway_Panther',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_Panther',
                      nThreads = 8)
ora_Panther <- ora_Panther[order(ora_Panther$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_Panther[,c('description', 'enrichmentRatio')]))
```

### Reactome

```{r}
ora_Reactome <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'pathway_Reactome',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_Reactome',
                      nThreads = 8)
ora_Reactome <- ora_Reactome[order(ora_Reactome$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_Reactome[,c('description', 'enrichmentRatio')]))
```

### Wikipathway

```{r}
ora_Wikipathway <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'pathway_Wikipathway',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_Wikipathway',
                      nThreads = 8)
ora_Wikipathway <- ora_Wikipathway[order(ora_Wikipathway$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_Wikipathway[,c('description', 'enrichmentRatio')]))
```

### network_CORUM

```{r}
ora_CORUM <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'network_CORUM',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_CORUM',
                      nThreads = 8)
ora_CORUM <- ora_CORUM[order(ora_CORUM$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_CORUM[,c('description', 'enrichmentRatio')]))
```

### CORUMA

```{r}
ora_CORUMA <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'network_CORUMA',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_CORUMA',
                      nThreads = 8)
ora_CORUMA <- ora_CORUMA[order(ora_CORUMA$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_CORUMA[,c('description', 'enrichmentRatio')]))
```

### phenotype_Human_Phenotype_Ontology

```{r}
ora_Phenotype <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'phenotype_Human_Phenotype_Ontology',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_Phenotype',
                      nThreads = 8)
ora_Phenotype <- ora_Phenotype[order(ora_Phenotype$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_Phenotype[,c('description', 'enrichmentRatio')]))
```

### community-contributed_MuscleGeneSets_Duddy_2017

```{r}
ora_MuscleGeneSets <- WebGestaltR(interestGene = DEgene,
                      referenceGene = Allgene,
                      interestGeneType = "ensembl_gene_id",
                      referenceGeneType = "ensembl_gene_id",
                      enrichMethod = "ORA",
                      organism = "hsapiens",
                      enrichDatabase = 'community-contributed_MuscleGeneSets_Duddy_2017',
                      sigMethod = "fdr",
                      fdrMethod = "BH",
                      fdrThr = 0.05,
                      reportNum = 30,
                      minNum = 5,
                      maxNum = 2000,
                      isOutput = TRUE,
                      outputDirectory = repor_dir,
                      projectName = 'DEXSeq_geneFDR0.01_ORA_MuscleGeneSets',
                      nThreads = 8)
ora_MuscleGeneSets <- ora_MuscleGeneSets[order(ora_MuscleGeneSets$enrichmentRatio, decreasing = T),]
knitr::kable(head(ora_MuscleGeneSets[,c('geneSet', 'enrichmentRatio')]))
```

```{bash, include=F, eval=T}
rename.ul 'Project_' "" results/reports/WebGestaltR/Project_*
```
